A multiverse analysis of the associations between internet use and well-being

### 2023-11-13 ms.Rmd
Improve reproducibility

---
title: 'A multiverse analysis of the associations between internet use and well-being'
shorttitle: Internet and well-being
leftheader: Internet and well-being
author: 
  - name: Matti Vuorre
    affiliation: "1,2"
    corresponding: yes
    address: Tilburg University
    email: m.j.vuorre@tilburguniversity.edu
  - name: Andrew K. Przybylski
    affiliation: "2"
    email: andy.przybylski@oii.ox.ac.uk
affiliation:
  - id: 1
    institution: Tilburg School of Social and Behavioral Sciences, Tilburg University
  - id: 2
    institution: Oxford Internet Institute, University of Oxford
authornote: |
  \noindent \textbf{This manuscript is not yet peer-reviewed. The preprint is available at https://psyarxiv.com/jp5nd/}
  We used the proprietary Gallup World Poll dataset, which is available to subscribing institutions through the Gallup website. All our code and a simulated GWP dataset is available at https://doi.org/10.5281/zenodo.7774923. We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database (with the exclusions detailed below). This study was not pre-registered.
keywords: well-being, internet technology, technology effects
wordcount: "4,217"
bibliography: references.bib
floatsintext: yes
linenumbers: no
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
documentclass: apa7
classoption: doc
header-includes:
  - |
    \setlength{\parskip}{0pt}
    \setlength\parindent{24pt}
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
    keep_tex: false
---

@@

# Parallel computation options
MAX_CORES <- as.numeric(
  Sys.getenv(
    "MAX_CORES", 
    unset = parallel::detectCores(logical = FALSE)
  )
)
CORES <- MAX_CORES - 2
theme_set(
  theme_linedraw(base_size = 9.6) +
    theme(
      strip.background = element_rect(fill = "gray90", color = "gray90"),
      strip.text = element_text(color = "black", hjust = 0),
      panel.grid = element_blank()
    )
)

@@

path <- "data-raw/gwp.rds"
if (dir.exists("data-raw/gallup") & !file.exists(path)) {

@@

  library(haven)
  library(labelled)
  # Load relevant variables
  dat <- read_spss(
    "data-raw/gallup/The_Gallup_042722.sav", 
    col_select = c(
      WGT,
      WP5, 
      YEAR_CALENDAR,
      WP1220,
      WP1219, 
      WP3117,
      WP23, 
      WP1223, 
      EMP_2010,
      INCOME_2,
      WP2319,
      WP16056,
      WP39,
      WP19544,
      WP15862,
      all_of(
        unlist(ix)
      )
    )
  )

@@

  # Save
  write_rds(dat, path)
}
```

```{r}
#| label: data-synth-create
#| eval: false

# Here we create a synthetic smaller dataset that mimics some statistical properties of the dataset. It is a smaller dataset because generating the full table is very slow.
if (FALSE) {
  dir.create("synthetic-data", FALSE)
  library(synthpop)
  set.seed(909090)
  x <- read_rds(path)
  x <- x %>% 
    filter(year > 2013) %>% 
    filter(country %in% sample(unique(x$country), 20)) %>% 
    # drop_na(starts_with("internet")) %>% 
    slice_sample(n = 200, by = country)
  x <- tibble(syn(x, method = "sample")$syn)
  write_csv(x, "synthetic-data/synthetic-data.csv.gz")
}
```

```{r}
#| label: data-load
dat <- read_rds(path)
# dat <- read_csv("synthetic-data/synthetic-data.csv.gz") # Synthetic dataset

@@

dir.create("tmp", FALSE)
path <- "tmp/multiverse-lmer.rds"
if (!file.exists(path)) {

  library(furrr)
  plan(multisession, workers = CORES)

@@

}
```

```{r}
#| Label: multiverse-tidy
specs <- readRDS(path) # Load from file

>>>>

---
title: 'A multiverse analysis of the associations between internet use and well-being'
shorttitle: Internet and well-being
leftheader: Internet and well-being
author: 
  - name: Matti Vuorre
    affiliation: "1,2"
    corresponding: yes
    address: Tilburg University
    email: mjvuorre@uvt.nl
  - name: Andrew K. Przybylski
    affiliation: "2"
    email: andy.przybylski@oii.ox.ac.uk
affiliation:
  - id: 1
    institution: Tilburg School of Social and Behavioral Sciences, Tilburg University
  - id: 2
    institution: Oxford Internet Institute, University of Oxford
authornote: |
  \textbf{This manuscript is not yet peer-reviewed. The preprint is available at \url{https://psyarxiv.com/jp5nd/}.}
  We used the proprietary Gallup World Poll dataset, which is available to subscribing institutions through the Gallup website. All our code and a simulated GWP dataset is available at \url{https://doi.org/10.5281/zenodo.7774923}. We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database (with the exclusions detailed below). This study was not pre-registered.
keywords: well-being, internet technology, technology effects
wordcount: "4,217"
bibliography: references.bib
floatsintext: yes
linenumbers: no
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
documentclass: apa7
classoption: doc
header-includes:
  - |
    \setlength{\parskip}{0pt}
    \setlength\parindent{24pt}
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
    keep_tex: false
---

@@

# Environment options
DATA_PATH_GWP <- Sys.getenv(
  "DATA_PATH_GWP"
)
DATA_PATH_GWP_CLEAN <- "data-raw/gwp.rds"
DATA_PATH_SYN <- Sys.getenv(
  "DATA_PATH_SYN",
  unset = "data-synthetic/synthetic-data.rds"
)
MAX_CORES <- as.numeric(
  Sys.getenv(
    "MAX_CORES", 
    unset = parallel::detectCores(logical = FALSE)
  )
)

# Figure theme
theme_set(
  theme_linedraw(base_size = 9.6) +
    theme(
      strip.background = element_rect(fill = "gray90", color = "gray90"),
      strip.text = element_text(color = "black", hjust = 0),
      panel.grid = element_blank()
    )
)

@@

# Wrangle GWP .sav file
if (file.exists(DATA_PATH_GWP) & !file.exists(DATA_PATH_GWP_CLEAN)) {

@@

  library(haven)
  library(labelled)
  # Load relevant variables
  dat <- read_spss(
    DATA_PATH, 
    col_select = c(
      WGT,
      WP5, 
      YEAR_CALENDAR,
      WP1220,
      WP1219, 
      WP3117,
      WP23, 
      WP1223, 
      EMP_2010,
      INCOME_2,
      WP2319,
      WP16056,
      WP39,
      WP19544,
      WP15862,
      all_of(
        unlist(ix)
      )
    )
  )

@@

  # Save
  write_rds(dat, DATA_PATH_GWP_CLEAN)
}
```

```{r}
#| label: data-synth-create

# Create synthetic smaller dataset for code reproducibility.
if (!file.exists(DATA_PATH_SYN)) {
  dir.create(dirname(DATA_PATH_SYN), FALSE)

  renv::settings$ignored.packages(c("synthpop", "mice"))
  library(synthpop)
  library(mice)

  set.seed(909090)
  data_synthetic <- read_rds(DATA_PATH_GWP_CLEAN) %>% 
    filter(country %in% sample(unique(country), 20)) %>% 
    slice_sample(n = 200, by = country) %>% 
    mice(m = 1) %>% 
    complete() %>% 
    tibble()

  data_synthetic <- data_synthetic %>% 
    syn() %>% 
    pluck("syn") %>% 
    tibble()

  write_rds(data_synthetic, DATA_PATH_SYN)
}
```

```{r}
#| label: data-load

if (file.exists(DATA_PATH_GWP_CLEAN)) {
  message("\n---\nUsing real data\n---\n")
  dat <- read_rds(DATA_PATH_GWP_CLEAN)
} else {
  message("\n---\nUsing synthetic data\n---\n")
  dat <- read_rds(DATA_PATH_SYN)
}

@@

path <- "tmp/multiverse-lmer.rds"
dir.create(dirname(path), FALSE)
if (!file.exists(path)) {

  library(furrr)
  plan(multisession, workers = MAX_CORES)

@@

}

specs <- readRDS(path)
```

```{r}
#| Label: multiverse-tidy
